\TheTitle

### 2016-06-21 linvis.tex
Expand Figure 1
More Fixes
 - Under drawbacks, specifies that the continuous mining is only for validation, not
   required. (I've left notes where I made changes, accuracy should be checked)
 - Removed some of the implementation details about flask, python, and postgresql.
   I've left the api information, though it could probably be moved more into
   discussion to say that other developers can use what we've done via the api
 - Changed gitk picture

\begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/gitk.png}
        \caption{A sample DAG view of commits from Linux in Gitk. Commits point
                towards their ancestors and there is no clear path from the commit
                to the merge with the master branch. In fact, neither Gitk nor Git
                are capable of showing what commits were done in master.}
        \label{fig:gitk}
\end{figure}

@@

\begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/tree_zoom.png}
        \caption{Entire Reingold-Tilford Tree of a merge. This merge by Linus (73287a43cc79ca06629a88d1a199cd283f42456a) contains 1722 includes non-merge commits
                touching 239 modules and 1525 files.}
        \label{fig:zoomed_tree}
\end{figure}

@@

Bubble trees are useful for providing a clear visualization of hierarchical
data\cite{Boardman2000}. The bubble tree (Figure~\ref{fig:bubble_tree}) provides a
very clear picture of where a commit is located in the tree hierarchy. The currently
selected commit or merge is colored red, while non-selected merges use a shade of
blue and commits use white.  The depth of the blue colouring is dependent on how
deep in the hierarchy that node is. The root is the lightest blue, and the contained
merges are progressively darker.

@@

\tool was built using Nginx as the main web server, postgresql as the DBMS, and
Flask as the framework for generating the dynamic content.

Nginx is a high-performance, open source, scalable HTTP and mail server. It is designed with massive
scalability and multi-processing in mind. Instead of using request-driven threading,
Nginx uses an event-driven architecture, making it more scalable, proving itself as
being the web server behind large sites like Netflix, Hulu, GitHub, Tumblr, and many
other popular sites\footnote{\url{http://wiki.nginx.org/Main}}.

Postgresql is our DBMS of choice, providing fast results.

We chose the python micro-framework
Flask\footnote{\url{http://flask.pocoo.org/docs/0.10/}} for generating the dynamic
content. Working with flask is simple and easy, allowing us to work in Python.

\subsection{Extendability}

@@

The biggest challenge, however, is computing the merge-tree. Our heuristic only
applies to the Linux kernel repository, and only since July 2009. It is very likely
that the heuristic will not work with other repositories, specifically those with
fast-forward commits into the master branch (a majority of repositories). We can
address the lack of information by monitoring the state of the repository at short
intervals as we did in \cite{German2015}. This continuous mining of the repository
requires foresight and planning.

@@

The tree model requires more information than what is provided by Git, requiring a
central server to monitor changes to the project. This breaks the design goals of
decentralized version control systems and makes the visualization tool specific to
the project.

>>>>

\begin{figure*}
        \centering
        \includegraphics[width=0.97\textwidth]{figures/gitk.png}
        \caption{A view of the Gitk interface centered on merge
          b34870fc9ff15fe46c4066faeeec437a4e63e2d8 by Miller. Commits point toward
          their ancestors and there is no clear path from the commit to the merge
          with the master branch. Neither Gitk nor Git are capable of showing the
          commits in master.}
        \label{fig:gitk}
\end{figure*}

@@

\begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/tree_zoom.png}
        \caption{The complete Reingold-Tilford tree of a merge by Linus
          (73287a43cc79ca06629a88d1a199cd283f42456a) containing 1722 non-merge
          commits touching 239 modules and 1525 files.}
        \label{fig:zoomed_tree}
\end{figure}

@@

Bubble trees are useful for providing a clear visualization of wide, hierarchical
data\cite{Boardman2000}. The tree structure is represented by the nesting of nodes;
the largest circle is the root, containing all the other nodes. The smallest circles
do not contain any nodes and therefore represent the leaf nodes.

Our implementation of the bubble tree (Figure~\ref{fig:bubble_tree}) provides the
user with a clear picture of where a commit is located in the merge tree. We
highlight the selected commit or merge in red. Non-selected merges are in a shade of
blue determined by the depth of a node in the tree. The root is the lightest shade
of blue, while the contained merges are progressively darker; the commits are white.

@@

\evantodo{See if we can move API section to be part of another section}

@@

\evan{Check accuracy of this paragraph}

The biggest challenge is computing the merge-tree of the Linux kernel repository. It
is likely that our heuristic for computing the merge-tree will not work with other
repositories. The heuristic requires that there are no fast-forward merges into the
master branch of the repository (a majority of repositories), and that there are no
foxtrot merges. We are able to use our heuristic with the Linux kernel because of
the strict integration model imposed by Linus. To validate the results of the
heuristic, we use the continuous mining technique described in \cite{German2015}.
The continuous mining of the repository requiring foresight and planning.

@@

\evan{Check the validity of this paragraph}
We use a heuristic method to generate the tree from the repository. The heuristic
requires that the repository does not have fast-forward merges into the master
branch or foxtrot merges, which obfuscate the master branch. In either case, the
heuristic will break and result in a tree that does not accurately represent the
repository. Validation of the results from the heuristic requires continuous mining
of the repository.
